A user-extensible and adaptable parser architecture

### 2008-05-14 papers/sgai-2008/paper.tex
Skeleton for Carl to read.

\title{Using Decision Trees for optimisation rather than classification
XXX BETTER TITLE}
\author{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \&
vogel@cs.tcd.ie }
\maketitle

@@

    Classification performed by evaluating user-defined sequences of tests
    can be optimised by applying a Decision Tree algorithm to data gathered
    from running the tests, providing the user with a more efficient or
    more accurate sequence of tests.  This usage of Decision Trees is
    illustrated by optimising Postfix~\cite{postfix} anti-spam
    restrictions~\cite{smtpd_access_readme}, a task complicated by the
    division of the tests into groups, restricting the Decision Tree
    algorithm to examining subsets of attributes at a time.

@@

Motivation, background on Postfix restrictions (appendix maybe?)

@@

Standard CART Decision Tree with modifications:

\begin{itemize}

    \item groups of attributes to examine

    \item result already known --- non-rejections will be weeded out into
        the false branches, eventually ending up in the bottom-left-most
        leaf node.

    \item scoring functions

\end{itemize}

@@

\begin{itemize}

    \item duplicate rows collapsed; histograms of distribution

    \item optimised ordering --- primary component analysis

    \item image

    \item different trees from different scoring functions

\end{itemize}

@@

Useful for optimisation and visualisation.

@@

>>>>

\title{A user-extensible and adaptable parser architecture}
\author{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \&
vogel@cs.tcd.ie }
\maketitle

@@

    Some parsers need to be very precise and restrictive in what they
    parse, yet allow users to easily adapt existing rules or add new rules
    to parse new inputs, without requiring an in-depth knowledge of the
    parser's internal workings.  This paper presents a novel parsing
    architecture which aims to make the process of parsing new inputs as
    simple as possible, enabling users to trivially add new rules (to parse
    variants of existing inputs) and relatively easily add new actions (to
    do something useful with a previously unknown class of input).

@@

Background of the project --- emphasise the variety in the log lines.
Motivation for creating the parser.  At some point I want to compare this
architecture to recursive decent parsers, Lex/Yacc parsers, XXX parsers.

@@

Split into framework, actions, \& rules.  Explain adding new rules and
actions.  Cut down rules to the minimum possible.  Framework provides
support functions, parsing loop, manages data --- boring stuff users don't
need to concern themselves with.

@@

Scalability, ordering, caching regexes.  Interesting to run with all rules
versus running with the minimum number necessary to parse the test log
files.  Then try that again with different orderings?

@@

Makes adding new rules trivial, new actions tractable.  Knowledge of the
framework is rarely necessary.

@@

\cite{postfix}
